ProbabilityBoundsAnalysis.jl:\\ Arithmetic with sets of distributions

### 2021-11-08 paper/header.tex
fixes minor typos

\hypersetup{
pdftitle = {ProbabilityBoundsAnalysis.jl:\\ an Arithmetic of probabilities and sets of probabilities},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Ander Gray, Scott Ferson, Edoardo Patelli},
pdfkeywords = {Julia, Uncertainty, Interval Arithmetic, Probability Bounds Analysis, Probability Boxes},
}

>>>>

\hypersetup{
pdftitle = {ProbabilityBoundsAnalysis.jl: Arithmetic with sets of distributions},
pdfsubject = {JuliaCon 2019 Proceedings},
pdfauthor = {Ander Gray, Scott Ferson, Edoardo Patelli},
pdfkeywords = {Julia, Uncertainty, Interval Arithmetic, Probability Bounds Analysis, Probability Boxes},
}

### 2021-11-08 paper/paper.tex
fixes minor typos

An uncertain programming language would require \textit{source-to-source} transformations at times. For example, one way to evaluate a programs control-flow (\texttt{if-else} conditions) with uncertain inputs is to use metaprogramming. The programs control flow could be unraveled, and with each possible conditional branch evaluated for the possible instance of the variable, and then combined as an output. For example consider following function

@@

where the integration domain is the set $L\{z\} = \{(x,y)| x,y \in \mathbb{R}, L(x,y) < x\}$ (the set of all $x$ and $y$ for which $L(x,y) < z$), and where $L$ is some binary operation (e.g. $L(x,y) = x+y$). The above $\sigma_{C,L}$ convolution is written for precise distributions, however can be extended for p-boxes by performing the convolution with some combination of the p-boxes bounds in the style of interval arithmetic:

>>>>

An uncertain programming language would require \textit{source-to-source} transformations at times. For example, one way to evaluate a programs control-flow (\texttt{if-else} conditions) with uncertain inputs is to use metaprogramming. The programs control flow could be unraveled, and with each possible conditional branch evaluated for the possible instance of the variable, and then combined as an output. For example consider the following function

@@

where the integration domain is the set $L\{z\} = \{(x,y)| x,y \in \mathbb{R}, L(x,y) < z\}$ (the set of all $x$ and $y$ for which $L(x,y) < z$), and where $L$ is some binary operation (e.g. $L(x,y) = x+y$). The above $\sigma_{C,L}$ convolution is written for precise distributions, however can be extended for p-boxes by performing the convolution with some combination of the p-boxes bounds in the style of interval arithmetic:
